Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-09-08 texor.Rmd
using one r chunk for figure

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor.", out.width="90%", fig.align='center'}
knitr::include_graphics("workflow.png")
```

>>>>

```{r workflow, fig.cap="Workflow of the document conversion conducted by texor.", out.width="90%", fig.align='center'}
#
if (knitr::is_html_output()) {
  library(DiagrammeR)
  DiagrammeR::mermaid(diagram = "flowchart TD
    A[Original Article] --> |Pre processing in R| B[Pre-Processed Article]
    B --> |pandoc reader|C{AST} 
    C -->|pandoc writer| D[Converted Article]
    C -->|modify AST using lua filter| C{AST}")
}
if (knitr::is_latex_output()) {
  knitr::include_graphics("workflow.png")
}
```
